### 2015-03-12 ResearchNotes/Notes.Rmd
Very basic KWH model with a few graphics about setpoints by race.

summary(RECS)

@@

the weights are a little odd, too large differences.  Investigate the top end to find.
```{r}
summary(RECS[RECS$NWEIGHT>40000,])

@@

>>>>

#summary(RECS)

@@

the weights are a little odd, too large differences.  Investigate the top end to find.
```{r}
#summary(RECS[RECS$NWEIGHT>40000,])

@@

That should finish the data wrangling.

# Electricity Model

A really basic model
```{r}

summary(lm(KWH~TOTSQFT_EN:HDD65+TOTSQFT_EN:CDD65 +Householder_Race+KOWNRENT:TYPEHUQ, data=RECS))

Time to kill those living for free and with the crazy large weights
```{r}

summary(lm(KWH~TOTSQFT_EN:HDD65+TOTSQFT_EN:CDD65 +Householder_Race:Hispanic+KOWNRENT:TYPEHUQ, data=RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000,]))

```
May have to chunk that up a bit

Time to see if the behaviors are different, all exogenous.  Checking temperatures

Here are the winter temps
```{r}
boxplot(TEMPHOME~Householder_Race, notch=TRUE,data=RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000,])

```{r}
boxplot(TEMPGONE~Householder_Race, notch=TRUE,data=RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000,])

```{r}
boxplot(TEMPNITE~Householder_Race, notch=TRUE, data=RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000,])

and the summer temps
```{r}
boxplot(TEMPHOMEAC~Householder_Race, notch=TRUE, data=RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000,])

```{r}
boxplot(TEMPGONEAC~Householder_Race, notch=TRUE, data=RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000,])

```{r}
boxplot(TEMPNITEAC~Householder_Race, notch=TRUE, data=RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000,])

There are differences and it looks like AA are more energy intensive with respect to setpoints

Checking TV use

```{r}
xtabs(~RECS$TVONWD1+RECS$Householder_Race, data=RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000,])
